volleyball dataset

### 2022-10-12 inst/volleyball.Rmd
labels

```{r}
volleyball <- volley(volleyball_table)
(volleyball_maxp <- maxp(volleyball))
```

@@

```{r}
zipf <- function(n){jj <- 1/(1:n); jj/sum(jj)}
zipf(9)
(null_support <- loglik(indep(zipf(9)),volleyball))
(alternative_support <- loglik(indep(volleyball_maxp),volleyball))
(Lambda <- 2*(alternative_support-null_support))
pchisq(Lambda,df=8,lower.tail=FALSE)
```

@@

```{r,label=savecurlingdataset}
save(volleyball_table,volleyball_maxp,volleyball,file="volleyball.rda")
```

>>>>

```{r calcmaxpvolley}
volleyball <- volley(volleyball_table)
(volleyball_maxp <- maxp(volleyball))
```

@@

```{r zipflikelihood}
zipf <- function(n){jj <- 1/(1:n); jj/sum(jj)}
zipf(9)
(null_support <- loglik(indep(zipf(9)),volleyball))
(alternative_support <- loglik(indep(volleyball_maxp),volleyball))
(Lambda <- 2*(alternative_support-null_support))
pchisq(Lambda,df=8,lower.tail=FALSE)
```

@@

```{r,label=savevolleyballdataset}
save(volleyball_table,volleyball_maxp,volleyball,file="volleyball.rda")
```
